University of Florida Knowledge Base Acceleration Notebook

### 2013-10-24 paper/kbanotebook2013/content/results.tex
added changes removed some coloquial sentences

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was composed of a single node cluster, which we refer to as the
 \textit{server}; the configuration of which is as described in
 Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English.
 Each document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
The total size of the data after XZ compression and GPG encryption is 4.5TB and
just over 500M StreamItems \cite{s3}. Data is stored in directories the naming
of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am)
until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952
date-hour combinations. This corpora consists of various media types the
distribution of which can be found in Table~\ref{table:documentsDist}. To have a
sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields. The first portion of the data which 
ranges from October 2011 to February 2012 is considered as training data.
The source code of our system is stored as an open source project where
enthusiasts can also contribute to \cite{github}, also the relevant discussion
mailing list is accessible here \cite{googlegroups}.

\begin{table}[b]
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

@@

\begin{table}    
\caption{ Recall Measure on \textit{submission\_infer}: Generic slot names like affiliate had the most recall, compared to less popular slot names e.g. DateOfDeath }
\centering
\label{table:finalresultrecall}
\begin{tabular}{|c|p{3.5cm}|p{4cm}|}
\hline 
 \textbf{Slot Name} & \textbf{Total instances of slot value found} & \textbf{\# of entities covered by slot value} \\ 
\hline 
Affiliate & 108598 & 80 \\ \hline 
AssociateOf & 25278 & 106 \\ \hline 
AwardsWon & 38 & 14 \\ \hline 
CauseOfDeath & 0 & 0 \\ \hline 
Contact\_Meet\_Entity & 191 & 8 \\ \hline 
Contact\_Meet\_PlaceTime & 5974 & 109 \\ \hline 
DateOfDeath & 87 & 14 \\ \hline 
EmployeeOf & 75 & 16 \\ \hline 
FoundedBy & 326 & 30 \\ \hline 
FounderOf & 302 &  29 \\ \hline 
Titles & 26823 & 118 \\ \hline 
TopMembers & 314 & 26 \\ \hline

\begin{table}
\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something }
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|c|c|c|c|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline

>>>>

%\ceg{We can add data on the total document size, The %number of each document type.  } 
 Our system was developed on a 32-core server described in
 Table~\ref{table:serverspec}. The corpus is a snapshot of the web in English.
 Each document is annotated using lingpipe and is called StreamItem, a bundle of 
StreamItems are put together and serialized as Apache Thrift objects, then 
compressed using xz compression with Lempel–Ziv–Markov chain algorithm (LZMA2) 
and finally encrypted using GNU Privacy Guard (GPG) with RSA asymmetric keys.
The total size of the data after XZ compression and GPG encryption is 4.5TB and
just over 500M StreamItems \cite{s3}. Data is stored in directories the naming
of which is date-hour combination: from 2011-10-05-00 (5th of October 2011, 12am)
until 2013-02-13-23 (13th of Feburary 2013, 11pm), which consists of 11952
date-hour combinations. This corpora consists of various media types the
distribution of which can be found in Table~\ref{table:documentsDist}. To have a
sense of the scale of objects and compression as an example a 6mb
gpg.xz files would become 45 mb thrift objects which can contain a couple of 
thousand StreamItems depending on their size. Some of the documents have null 
values for their annotation fields. The first portion of the data which 
ranges from October 2011 to February 2012 is considered as training data.
The source code of our system is stored as an open source project where
enthusiasts can also contribute to \cite{github}, also the relevant discussion
mailing list is accessible here \cite{googlegroups}.

\begin{table}
\caption{Document Chunks Distribution }
\centering
\label{table:documentsDist}

@@

\begin{table}
\caption{SSF Accuracy Measure on \textit{submission\_infer}: Accuracy of AffiliateOf was the best and Affiliate applied poorly due to ambiguity of being an affiliate of somebody/something}
\centering
\label{table:finalresultaccuracy}
\begin{tabular}{|l|c|c|c|}
\hline 
 \textbf{Slot Name}  & \textbf{Correct} & \textbf{Incorrect Entity name} & \textbf{Incorrect Value} \\ 
\hline 
Affiliate & 1\% & 95\% & 5\% \\ \hline 
AssociateOf & 63.6\% & 9.1\% & 27.3\%  \\ \hline 
AwardsWon & 10\% & 10\% & 80\%  \\ \hline 
CauseOfDeath & 0\% & 0\% & 0\%  \\ \hline 
Contact\_Meet\_Entity & 21\% & 42\% & 37\%  \\ \hline 
Contact\_Meet\_PlaceTime & 5\% & 20\% & 85\%  \\ \hline 
DateOfDeath & 29.6\% & 71\% & 25\%  \\ \hline 
EmployeeOf & 5\% & 30\% & 65\%  \\ \hline 
FoundedBy & 62\% & 17\% & 21\%  \\ \hline 
FounderOf & 50\% & 0\% & 50\%  \\ \hline 
Titles & 55\% & 0\% & 45\%  \\ \hline 
TopMembers & 33\% & 17\% & 50\%  \\ \hline
